The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction

### 2024-02-13 outputs/paper/paper.qmd
rewrote draft intro and data section

---
title: "Shaping Future Wealth: Analyzing Lifetime Resources Among Norway's Young Adults (25-40)"
subtitle: "My subtitle if needed"
author: 
  - Sami El Sabri
  - Liban Timir
thanks: "Code and data are available at: https://github.com/samielsabri/reproduce_paper"
date: 02-13-2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

# Introduction

@@

>>>>

---
title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
subtitle: "My subtitle if needed"
author: 
  - Sami El Sabri
  - Liban Timir
thanks: "Code and data are available at: https://github.com/samielsabri/reproduce_paper"
date: 02-13-2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

install.packages("ggplot2")

library(ggplot2)

gitcreds_set()
```

# Introduction
In the evolving landscape of organizational psychology, the exploration of individual agency beliefs (particularly free will) and their impact on job satisfaction presents a compelling field of study. "Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction" by Feldman et al. embarks on this journey, unveiling the nuanced relationship between one's belief in free will and their subsequent job satisfaction across diverse cultural contexts. A focused exploration of this relationship within the context of the American workforce provides a valuable estimand, given the United States' strong emphasis on individualism, autonomy, and the freedom to shape one's destiny which are principles deeply ingrained in the national ethos.

The paper addresses a significant gap in existing literature by articulating how free will beliefs, beyond serving as philosophical contemplations, exert a tangible influence on individuals' professional lives. Through a robust approach that includes longitudinal studies and cross-cultural analyses, the research highlights a consistent positive correlation between strong beliefs in free will and higher levels of job satisfaction. This relationship, significantly influenced by perceived autonomy, underscores the pivotal role of individual agency beliefs in the context of the American workplace, where personal freedom and self-determination are highly valued.

The importance of this paper lies not only in its findings but also in its implications, offering practical insights for enhancing organizational culture and employee satisfaction within the American context. By highlighting the importance of fostering environments that champion autonomy and respect individual agency beliefs, the paper prompts business leaders and policymakers to rethink strategies for workplace management and development. This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.

Structurally, the paper unfolds starting from its comprehensive methodology (including the six-month study of American online workers) to its extensive cross-cultural survey, which contextualizes the American data within a global framework. It then articulates the specific implications of free will beliefs for job satisfaction among American employees, weaving these insights into broader discussions on the interplay between cultural values, individual beliefs, and workplace dynamics. The concluding sections propose future research directions and practical applications, emphasizing the critical role of understanding and leveraging individual agency beliefs in cultivating a more motivated and satisfied workforce.

@@

The dataset for the study provides a detailed snapshot of free will beliefs, job satisfaction, and perceived job autonomy among American online workers.

The variables within this dataset were carefully selected to reflect key indicators of job satisfaction, belief in free will, job autonomy, and additional agency constructs for regional analysis within America.

Data cleaning was especially important in this case, considering the challenges inherent in longitudinal and generational health data. This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records. The dataset underwent meticulous cleaning, addressing missing values and ensuring consistency across responses. Special attention was given to the reliability of scales used for measuring the core variables, with adjustments made to account for the online work setting of the participants.

Summary statistics revealed the mean and median job satisfaction rates, the correlation in job autonomy, and other job-related metrics. This aggregated data provided a foundation for understanding the base conditions of the workplace and any preliminary patterns indicating the persistence of individual agency.

Visual representations, such as graphs and tables, illustrated the distribution of job satisfaction, free will beliefs, and the relationship between the two. These visuals helped to convey the depth and nuances of the autonomy persistence observed in the American data.

The appendices include detailed statistical tables, additional graphs showing complex data relationships, and extensive notes on the data cleaning and processing methodology.

This description of the dataset was written with the general ethical practices of demographic research in mind and provides a narrative for a subset of data focused on America.

The precise quantification of child mortality rates captured not only the incidence of deaths but also the timing and causes. This entailed using measurement techniques and standard demographic health indicators like the under-five mortality rate (U5MR) or neonatal mortality rate (NMR), which are internationally recognized measures.

Socioeconomic status was gauged using a composite index combining variables such as income, education, and occupation. These measurements were tailored to the Moroccan context to accurately reflect local economic conditions and societal structures.

Demographic characteristics were measured using standard metrics such as age, sex, household size, and variables that capture migration or urban-rural residency, given Morocco's diverse landscape from bustling cities to rural areas.

Measurement in this dataset was meticulous to ensure comparability across generations. For example, the paper needed to account for changes over time in how mortality or socioeconomic status is recorded and reported within Morocco. The potential for measurement error or bias would necessitate rigorous validation techniques, such as cross-referencing with other data sources or conducting field verifications.

The dataset also included constructed variables, which are derived from raw data through transformations or computations to better capture the concepts under study. For instance, a constructed variable might be a mortality risk score that combines the number of sibling deaths with the ages at which they occurred.

In the context of Morocco, the discussion of measurement would also address the cultural and linguistic considerations in the data collection process. Questionnaires and surveys needed to be accurately translated and culturally adapted to ensure the measurement is valid and reliable across different Moroccan communities.

Incorporating a thorough discussion of measurement in relation to the dataset is essential to validate the paper's findings and to ensure that conclusions drawn are based on accurate and reliable data. This discussion would ultimately contribute to the paper's credibility and the robustness of its policy recommendations for Morocco.
